Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2021-06-23 doc/manuscript/ESSDmanuscript.tex
updating table

>>>>

\caption{\label{tab:table_ForCfieldmapping}\textbf{Mapping of ForC fields to EFDB.}}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
\hline
\textbf{ForC table} & \textbf{ForC field} & \textbf{EFDB field} & \textbf{Use} & \textbf{Required}\\
\hline
Sites &  &  &  & \\
\hline
Measuremennts & variable.name & - & link to variable info in ForC\_variables table & y\\
\hline
 & mean & Value & (direct) & y\\
\hline
 & mean.in.original.units & Value in Common Units & (direct) & y\\
\hline
 & original.units & Common Unit & (direct) & y\\
\hline
 & sd, se, lower95\%CI, upper 95\%CI &  &  & y\\
\hline
 &  &  &  & \\
\hline
 & data.location.within.source &  & confirm that data weren't digitized, facilitate finding data in original publication & y\\
\hline
PFT & description &  &  & \\
\hline
variables & units &  &  & y\\
\hline
Citations & (several fields) &  &  & \\
\hline
\end{tabu}
\end{table}
